\ttitle

### 2013-11-18 Chapters/Chapter5/artificial_data_generation.tex
Rename  dir to

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/camci_fixed_increasing_mean.eps}
  \caption[Fixed increasing mean]{Fixed increasing mean}
  \label{fig:camci_fixed_increasing_mean}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/camci_fixed_increasing_mean_thresholds.eps}
  \caption[Fixed increasing mean, thresholds]{Fixed increasing mean, thresholds}
  \label{fig:camci_fixed_increasing_mean_thresholds}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/takeuchi_reduced_increasing_mean.eps}
  \caption[Reduced increasing mean]{Reduced increasing mean}
  \label{fig:takeuchi_reduced_increasing_mean}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/takeuchi_reduced_increasing_mean_thresholds.eps}
  \caption[Reduced increasing mean, thresholds]{Reduced increasing mean, thresholds}
  \label{fig:takeuchi_reduced_increasing_mean_thresholds}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/camci_reduced_increasing_mean_increasing_variance.eps}
  \caption[Reduced increasing mean, increasing variance]{Reduced increasing mean, increasing variance.}
  \label{fig:camci_reduced_increasing_mean_increasing_variance}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/camci_reduced_increasing_mean_increasing_variance_thresholds.eps}
  \caption[Reduced increasing mean, increasing variance, thresholds]{Reduced increasing mean, increasing variance, thresholds (log scale)}
  \label{fig:camci_reduced_increasing_mean_increasing_variance_thresholds}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/camci_takeuchi_alternating_variance.eps}
  \caption[Alternating variance]{Alternating variance}
  \label{fig:camci_takeuchi_alternating_variance}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/camci_takeuchi_alternating_variance_thresholds.eps}
  \caption[Alternating variance, thresholds]{Alternating variance, thresholds}
  \label{fig:camci_takeuchi_alternating_variance_thresholds}
\end{figure}

>>>>

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter5/camci_fixed_increasing_mean.eps}
  \caption[Fixed increasing mean]{Fixed increasing mean}
  \label{fig:camci_fixed_increasing_mean}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter5/camci_fixed_increasing_mean_thresholds.eps}
  \caption[Fixed increasing mean, thresholds]{Fixed increasing mean, thresholds}
  \label{fig:camci_fixed_increasing_mean_thresholds}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter5/takeuchi_reduced_increasing_mean.eps}
  \caption[Reduced increasing mean]{Reduced increasing mean}
  \label{fig:takeuchi_reduced_increasing_mean}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter5/takeuchi_reduced_increasing_mean_thresholds.eps}
  \caption[Reduced increasing mean, thresholds]{Reduced increasing mean, thresholds}
  \label{fig:takeuchi_reduced_increasing_mean_thresholds}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter5/camci_reduced_increasing_mean_increasing_variance.eps}
  \caption[Reduced increasing mean, increasing variance]{Reduced increasing mean, increasing variance.}
  \label{fig:camci_reduced_increasing_mean_increasing_variance}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter5/camci_reduced_increasing_mean_increasing_variance_thresholds.eps}
  \caption[Reduced increasing mean, increasing variance, thresholds]{Reduced increasing mean, increasing variance, thresholds (log scale)}
  \label{fig:camci_reduced_increasing_mean_increasing_variance_thresholds}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter5/camci_takeuchi_alternating_variance.eps}
  \caption[Alternating variance]{Alternating variance}
  \label{fig:camci_takeuchi_alternating_variance}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter5/camci_takeuchi_alternating_variance_thresholds.eps}
  \caption[Alternating variance, thresholds]{Alternating variance, thresholds}
  \label{fig:camci_takeuchi_alternating_variance_thresholds}
\end{figure}
